\huge Tor's Usability for Censorship Circumvention

### 2016-05-08 pets2017-paper/pets2017-paper.tex
Update conclusion.

We used this feedback to guide the redesign of the configuration interface. We test the impact of our changes on 116 participants. We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with reduction in success rates. {\color {red} TODO: add more here.} Our analysis suggests ways to improve the Tor interface as well as some potential opportunities for further research.

>>>>

We used this feedback to guide the redesign of the configuration interface. We test the impact of our changes on 116 participants. We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection and spent more of that time configuring the necessary components. We also discuss the common reasons for failing to connect to the Tor network, general behavioral trends of participants across conditions, make suggestions to to improve the Tor interface, and discuss potential opportunities for further research.
